Almost compatible functions and infinite length games

### 2015-12-04 articles/almost-compatible-functions-and-topological-games/article.tex
add abstract

\keywords{TODO}

% TODO
\subjclass[2010]{}

\begin{abstract}
  TODO
\end{abstract}

@@

  Weakening to the continuum hypothesis, we have an obvious consequence.

  \begin{corollary}[\(CH\)]
    \(\alcompSP{\aleph_2}\), but \(\neg\alcompS{\aleph_2}\).
  \end{corollary}

@@

  % TODO: read through Alan's proofs and fit to rest of document

>>>>

% \keywords{TODO}
% \subjclass[2010]{}

\begin{abstract}
  \(\alcompSP\kappa\) asserts the existence of pairwise
  almost compatible finite-to-one functions \(A\to\omega\) for each
  countable subset \(A\) of \(\kappa\).
  The existence of winning \(2\)-Markov strategies in
  several infinite-length games, including
  the Menger game on the one-point Lindel\"ofication \(\oneptlind\kappa\)
  of \(\kappa\), are guaranteed by \(\alcompSP\kappa\). \(\alcompSP\kappa\) is
  implied by the existence of cofinal Kurepa families of size \(\kappa\),
  and thus holds for all cardinals less than \(\aleph_\omega\).
  It's consistent that \(\alcompSP{\aleph_\omega}\) fails, but
  there must always be a winning \(2\)-Markov strategy for the second
  player in the Menger game on \(\oneptlind{\omega_\omega}\).
\end{abstract}

@@

  Weakening to the continuum hypothesis, we see an obvious consequence.

  \begin{corollary}[\(CH\)]
    \(\alcompSP{\mf c^+}\), but \(\neg\alcompS{\mf c^+}\).
  \end{corollary}

@@

  % Alan's results
